\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-20 paper.tex
Fixed typo

@@

Given that the main nodes on the Bitcoin network enforce a limit on the length of Script programs one can include in a transaction, guaranteed linear execution time results in an absolute maximum number of steps for a standard Script program. This helps in protecting against DoS attacks based on maliciously crafted transactions. Furthermore, this maximum number of steps was deliberately lowered by requiring that the most computationally expensive opcodes, \texttt{OP\_CHECKSIG}, be contained exactly once in a valid standard transaction [4].

>>>>

In this section, we use our grammar

@@

Given that the main nodes on the Bitcoin network enforce a limit on the length of Script programs one can include in a transaction, guaranteed linear execution time results in an absolute maximum number of steps for a standard Script program. This helps in protecting against DoS attacks based on maliciously crafted transactions. Furthermore, this maximum number of steps was deliberately lowered by requiring that the most computationally expensive opcode, \texttt{OP\_CHECKSIG}, be contained exactly once in a valid standard transaction [4].
